---
title: "Lobster Exploration"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(dplyr)
library(janitor)
library(here)
```


### Read in data
Read in data:
```{r}
lobsters <- read_csv(here("data","Lobster_Abundance_All_Years_20210412.csv"), na = c("-99999", "")) %>% 
  clean_names() %>% 
  uncount(count)
```

### Find counts and mean sizes by site & year
Create a summary table that finds the total counts (see: n()), and mean carapace lengths of lobsters observed in the data set by site and year.
```{r}
summary_table <- lobsters %>% 
  group_by(site, year) %>% 
  summarize(mean_size = mean(size_mm, na.rm = TRUE), n = n())
```

Create a ggplot graph of the number of total lobsters observed (y-axis) by year (x-axis) in the study, grouped (either aesthetically or by faceting) by site
```{r}
ggplot(data = summary_table, aes(x = year, y = n, group = site, color = site)) + geom_line()
```

### Find the proportion of legal lobsters at each site for 2020

The legal lobster size (carapace length) in California is 79.76 mm.
Create a subset that only contains lobster data from 2020 (note: this should be from the original data you read in, not the summary table you created above)

```{r}
lobsters_2020 <- lobsters %>% 
  filter(year == 2020)
```

Write code (you can decide how to do this - there are a number of ways) to find the counts of lobsters observed at each site (only using site as the grouping factor) that are above and below the legal limit. Hint: You may want to add a new column legal that contains “yes” or “no” based on the size of the observed lobster (see dplyr::case_when() for a really nice way to do this), then use group_by() %>% summarize(n()) or dplyr::count() to get counts by group within variables

```{r}
legal_lobsters_2020 <- lobsters_2020 %>% 
  
```














